\documentclass{article}
\usepackage{fullpage}
\usepackage[T1]{fontenc}
\usepackage{titling}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{amsmath}
\usepackage{amsfonts}

\setlength{\droptitle}{-8em}   % This is your set screw
\title{G\"odel Problem Set 2}
\date{Due: February 21, 2020}

\begin{document}
\maketitle

Answer each of the following problems.  As always, you must attempt
all of them.  This time, you must complete one of the easy problems and
one of the hard problems.  Your answers to completed problems must be
typeset in \LaTeX.  Good attempts can be hand written, bad attempts
must be delivered during lunch in Pearsons Hall in the form of
interpretive dance.

\section{Easy Problems that Look Hard}
\begin{enumerate}
\item Create a formal system of proof which is complete.  That is,
create a formal system under which all true propositions are provable.
Prove that your system does what you claim.  (And please, no
spoilers for anyone.  Let everyone sweat it out.)

\item Suppose I have two proof systems $\alpha$ and $\beta$.  Both systems
are $\omega$-consistent.  Suppose I have proposition $a$ 
which is undecidable in $\alpha$, and a different proposition $b$
which is undecidable in $\beta$.  Suppose I can use some function to
combine the two proof systems $\gamma=f(\alpha,\beta)$.  Can the
resultant system admit proofs of $a$ or $b$ and remain
$\omega$-consistent?  Prove your answer.

\end{enumerate}

\section{Hard Problems that Look Impossible}
\begin{enumerate}
\item Construct another C-undecidable number-theoretic proposition
(where C is some $\omega$-consistent formal system) that is
not equivalent to the G\"odel has given us.  Prove that your
proposition is undecidable under these constraints.  Extra points will
be awarded if your proposition can be decided outside of any formal
system (as was G\"odel's proposition.)

\item Fill in the outline of the proof presented in G\"odel's
proposition V. That is, present the formal proof which G\"odel describes
as not technically challenging, but terribly tedious.  (Believe me, it
is tedious.)
\end{enumerate}

\end{document}
